Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-07-06 paper_jasa.tex
proof reading

\hh{In order to compare power of conventional tests and lineups side-by-side, we will have to assume, that we are in the controlled environment of a simulation with tests corresponding to a known parameter value $\theta \in R$ and associated distribution function $F_t$ of the test statistic. }

@@

Table \ref{tbl:model_par} shows the parameter estimates of the mixed effects model of the subject-specific variation.  \green{What do we learn about the models from these parameter estimates? Explain this here too.}

\green{This section needs to have sufficient detail of the model fitting, output and diagnostics to feed into the next few sections discussing the findings.}

@@

>>>>

\hh{In order to compare power of conventional and visual tests side-by-side, we will have to assume, that we are in the controlled environment of a simulation with tests corresponding to a known parameter value $\theta \in R$ and associated distribution function $F_t$ of the test statistic. }

@@

Table \ref{tbl:model_par} shows the parameter estimates of the mixed effects model of the subject-specific variation. The larger variability in the response data for experiment 3 as we see in Figure \ref{fig:power_loess_effect} contributes the random effect variance estimate be much larger compared to those of other experiments. Because fo the same reason we see the standard error for intercept estimate is much higher as well. Also notice the slope estimate for experiment three is lowest as well. It is because for small parameter values the power is much higher for experiment 3.  % \green{What do we learn about the models from these parameter estimates? Explain this here too.}

%\green{This section needs to have sufficient detail of the model fitting, output and diagnostics to feed into the next few sections discussing the findings.}

@@

\blue{Another critical part is the specific question that the observer needs to answer evaluating the lineup. The question should be more than just asking to find the most different plot. Selecting the appropriate word to describe the pattern we may see when alternative hypothesis is true is important to help the observers understand what pattern they should look for. By delivering an appropriate question may reduce the type III error in an appropriate scenario.}
